### 2017-06-07 sheets/talk-6/sheet-6.tex
Sheet 6: Import exercises from the script

@@

>>>>

\begin{exercise}
  Let $\parpair{X}{Y}{s}{t}$ be maps in some category.  Prove that $s = t$ if
  and only if the equalizer of $s$ and $t$ exists and is an isomorphism, if
  and only if the coequalizer of $s$ and $t$ exists and is an isomorphism.
\end{exercise}

\begin{exercise}
  Let $X$ be a set and $f\from X \to X$ a map.  Describe the coequalizer of
  $\parpairi{X}{X}{f}{1}$ in $\Set$ as explicitly as possible.
\end{exercise}

@@

\begin{exercise}
  Take objects and maps $\xymatrix@1{E \ar[r]^i &X \ar@<.5ex>[r]^{f}
  \ar@<-.5ex>[r]_g &Y}$ in some category.  If this is an equalizer, is the
  square
  \[ \xymatrix{
    E \ar[r]^i \ar[d]_i &
    X \ar[d]^g \\
    X \ar[r]_f &
    Y
  } \]
  necessarily a pullback?
  What about the converse?  Give proofs or counterexamples.
\end{exercise}

\begin{exercise}
  Take a commutative diagram
  \[ \xymatrix{
    \cdot \ar[r] \ar[d] & \cdot \ar[r] \ar[d] & \cdot \ar[d] \\
    \cdot \ar[r] & \cdot \ar[r] & \cdot
  } \]
  in some category.  Suppose that the right-hand square is a pullback.  Show
  that the left-hand square is a pullback if and only if the outer rectangle is
  a pullback.
\end{exercise}
